Lineage Analysis of CRISPR and shRNA Screens

### 2018-09-03 lineages_18Q3.Rmd
replace old Rmd with new

dep_prob_5 <- ggplot(data = filter(crispr_data, Dep_Prob >= 0.95), aes(x = Dep_Prob)) +
  geom_histogram(mapping = aes(fill = primary_tissue), breaks = seq(0.95, 1, by = 0.005), color = "black") +
  scale_y_continuous(breaks = seq(0, 60000, by = 10000), labels = formatC(seq(0, 60000, by = 10000), format = "d")) +
  theme(legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 4, byrow = FALSE)) +
  stat_bin(breaks = seq(0.95, 1, by = 0.005), geom = "text", color = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
  labs(title = "Distribution of all dependency probabilities > 0.95", x = "Probability of Real Dependency", y = "Frequency", fill = "Primary Tissue")

dep_prob_inset <- dep_prob_100 + annotation_custom(ggplotGrob(dep_prob_5), xmin = 0.49, xmax = 0.99, ymin = 2500000, ymax = 5000000)

ggsave("./../crispr_lineages_giant_files/dependency_probability_inset.pdf", plot = dep_prob_inset, width = 12, height = 6, units = "in", device = "pdf")
```

>>>>

dep_prob_5 <- ggplot(data = filter(crispr_data, Dep_Prob >= 0.95), aes(x = Dep_Prob)) +
  geom_histogram(mapping = aes(fill = primary_tissue), breaks = seq(0.95, 1, by = 0.005), color = "black") +
  scale_y_continuous(breaks = seq(0, 60000, by = 10000), labels = formatC(seq(0, 60000, by = 10000), format = "d")) +
  theme(legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 4, byrow = FALSE)) +
  stat_bin(breaks = seq(0.95, 1, by = 0.005), geom = "text", color = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
  labs(title = "Distribution of all dependency probabilities > 0.95", x = "Probability of Real Dependency", y = "Frequency", fill = "Primary Tissue")
```
